{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-29 paper.tex
Mnetion QSRLib

\uwds provides a client ({\tt spatial\_relations}) to compute both
allo-centric and ego-centric (\ie viewer-dependent) spatial relations
between objects (Figure~\ref{fig|spatialrelations}).

>>>>

\uwds provides an exemplary client ({\tt spatial\_relations}) to compute both
allo-centric and ego-centric (\ie viewer-dependent) spatial relations
between objects (Figure~\ref{fig|spatialrelations}).
Other libraries, like QSRLib~\ref{gatsoulis2016qsrlib}, that implement
computational models of Qualitative Spatial Relations could be trivially
combined with \uwds to provide more advanced geometric analysis.
